### 2013-12-13 tests_Housing.Rmd
added datapoints with 'classic' EPR
ie, no regularization and all monoids are active. This is the closest
version we are able to in accordance to the algorithms from the
references.
added 'load' commands to tests_*.Rmd

save(report, file="Housing300_lambda0.8.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.txt")

>>>>

save(report, file="Housing300_lambda0.8_add_linears.Rda") # recover with load("Housing300.Rda")

load(file="Housing300_lambda0.8_add_linears.Rda")

load(file="Housing300_lambda1_allmonoids.Rda")

summary(report$ga.error)

@@

write.table(df, "Housing300_lambda0.8_add_linears.txt")

### 2013-12-13 tests_Kinematics.Rmd
added datapoints with 'classic' EPR
ie, no regularization and all monoids are active. This is the closest
version we are able to in accordance to the algorithms from the
references.
add new data points using linear add-ons
added 'load' commands to tests_*.Rmd

@@

save(report, file="Kinematics300_lambda0.8_25runs.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics200.txt")

>>>>

load(file="Kinematics300_lambda0.8_add_linears.Rda")
load(file="Kinematics300_lambda1_allmonoids.Rda")
summary(report$ga.error)

@@

save(report, file="Kinematics300_lambda0.8_add_linears.Rda") # recover with load("Kinematics.Rda")

@@

write.table(df, "Kinematics300_lambda0.8_add_linears.txt")
